%-------------------------
% Resume in Latex
% Author : Dushmanta Behera
% Based off of: https://github.com/dushmanta05/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%for social icons
\usepackage{fontawesome5}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%  RESUME STARTS HERE  %


\begin{document}

%----------HEADING----------

\begin{center}
   \textbf{\Huge \scshape Dushmanta Behera} \\ \vspace{1pt}
    \small 
    \raisebox{-0.05\height}{\faPhone*} \href{tel:+919556515251}{{(+91) 9556515251}} $|$ 
    \raisebox{-0.05\height}{\faEnvelope} \href{mailto:dushmanta0511@gmail.com}{{dushmanta0511@gmail.com}} $|$ 
    \raisebox{-0.05\height}{\faGithub} \href{https://github.com/dushmanta05}{{\underline{GitHub}}}
     $|$ 
    \raisebox{-0.05\height}{\faLinkedin} \href{https://www.linkedin.com/in/dushmanta05/}{{\underline{LinkedIn}}}
    $|$ 
    \raisebox{-0.05\height}{\faGlobe} \href{https://dushmanta.dev/}{{\underline{Portfolio}}}
    
    
\end{center}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
%-------------------------------------------
\resumeSubheading
      {Sofftware Developer Apprentice}{Jan 2024 - Ongoing}
      {HyScaler}{}
      \resumeItemListStart
      \resumeItem{Collaborated on the development of a CRM software using FilamentPHP within a Laravel environment along with PostgreSQL, ensuring efficient data management and seamless user interaction.}
       \resumeItem{Implemented a Laravel and MySQL-based hotel booking project, focusing on database optimization and user experience improvements.}
    \resumeItemListEnd
  \resumeSubheading
      {Junior Front-end Developer}{Sept 2023 - Jan 2023}
      {Webysis}{}
      \resumeItemListStart
       \resumeItem{Engineered a high-performance, responsive UI for the home page of the DoctoCart e-commerce app.}
        \resumeItem{Conducted thorough API testing to guarantee seamless data retrieval and rendering for a diverse array of medical equipment listings.}
         \resumeItem{Orchestrated the deployment of project code on GitHub, establishing robust version control practices and overseeing live website deployment.}
    \resumeItemListEnd
  \resumeSubheading
      {React.js Developer}{Dec 2022 - Apr 2023}
      {Invicta Ltd}{}
      \resumeItemListStart
       \resumeItem{Spearheaded the development of the e-commerce website's product page, focusing on optimizing user experience.}
        \resumeItem{Collaborated closely with the design team to seamlessly integrate visually captivating product displays, resulting in a significant boost in user engagement.}
         \resumeItem{Implemented user-centric CRUD operations, enhancing the interactive functionality of the product page.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\resumeItemListStart
            \resumeItem{\textbf{Languages}{: HTML5, CSS3, JavaScript, TypeScript, PHP, SQL, Markdown}}
            \resumeItem{\textbf{Technologies}{: React, NextJS, Laravel, LIvewire, jQuery, Tailwind, FilamentPHP, shadcn/ui, MaterialUI, Styled-Components, etc}}
            \resumeItem{\textbf{Tools}{: Git, GitHub, GitLab, ClerkAuth, Postman, Shopify, ViteJs, Webpack, npm/yarn, VScode, etc}}
\resumeItemListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{EduTek - LMS Platform}}
          {{ {\small {\faGithub} \href{https://github.com/dushmanta05/edutek}{\underline{GitHub}}} $|$ {\small {\faGlobe} \href{https://edutek.vercel.app/}{{\underline{Website}}}}}}
          \resumeItemListStart
            \resumeItem{Built a secure and efficient LMS platform using Next.js, with user authentication and Stripe integration for seamless enrollment.}
            \resumeItem{Developed a robust admin dashboard for course management, pricing settings, and analytics tracking.}
            \resumeItem{Crafted API routes for streamlined data retrieval and submission, hosting the database on Railway, and deploying the project on Vercel for optimal performance}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{GymBull - Gym Exercise App}}
          {{ {\small {\faGithub} \href{https://github.com/dushmanta05/gymbull}{\underline{GitHub}}} $|$ {\small {\faGlobe} \href{https://fit-bull.netlify.app/}{{\underline{Website}}}}}}
          \resumeItemListStart
            \resumeItem{Engineered a comprehensive gym exercise web application with advanced search functionalities.}
            \resumeItem{Employed modular components for customization, implemented intuitive navigation, and optimized performance through efficient bundling techniques.}
            \resumeItem{Successfully integrated an external API, seamlessly fetching and displaying data to enhance the application's content and functionality.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Trippz - Travelling Agency}}
          {{ {\small {\faGithub} \href{https://github.com/dushmanta05/trippz}{\underline{GitHub}}} $|$ {\small {\faGlobe} \href{https://trippz.vercel.app/}{{\underline{Website}}}}}}
          \resumeItemListStart
            \resumeItem{Designed and implemented a polished, responsive interface for a React-based website.}
            \resumeItem{Engineered dynamic and responsive user interfaces by skillfully crafting React components, seamlessly integrating React Router for efficient single-page application navigation.}
            \resumeItem{Implemented robust state management in React, fostering a smooth and reliable web experience grounded in responsive design principles.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%%
%-----------EDUCATION-----------
\section{Education} 
  \resumeSubHeadingListStart
    \resumeSubheading
      {Veer Surendra Sai University of Technology}{Sambalpur, Odisha}
      {Bachelor Of Technology in Electrical Engineering}{Aug 2015 -- June 2019}
       \resumeItemListStart
        \resumeItem{Cumulative GPA : {6.61/10.0}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
